An efficient acyclic contact planner for multiped robots

### 2017-01-05 body/intro.tex
merged andreas comment + updating validation code

Finally, to demonstrate the validity of our approach\deladp{ regarding the complete chain}, we show that the generated contact plans can be successfully executed, either in simulation or on the real HRP-2 robot.

>>>>

Finally, to demonstrate the validity of our approach \deladp{ regarding the complete chain}, we show that the generated contact plans  can be successfully executed (problem  $\mathcal{P}_3$), either in simulation or on the real HRP-2 robot.
